Jane, John … Leslie? A Historical Method for Algorithmic Gender Prediction

### 2014-09-29 article.Rmd
Note to add later
Order all bar plots female, unknown, male
This permits both male and female to be compared to the 0.5 line.

```{r}
diss_predicted %>%
  ggplot(aes(x = year, fill = gender_author)) + 
  geom_bar(binwidth = 1) +
  ggtitle("Dissertations about history by gender, 1950-2012") +
  xlab(NULL) + ylab(NULL) +
  short_scale + theme(legend.position = "bottom") +
  scale_fill_brewer(palette = article_palette, name = "",
                      labels = c("Female", "Male")) +
  article_theme
```

@@

diss_proportions  %>%
  ggplot(aes(x = year, y = proportion, fill = gender)) +
  geom_bar(binwidth = 1, stat = "identity") +
  ggtitle("Proportion of dissertations about history by gender, 1950-2012") +
  xlab(NULL) + ylab(NULL) +
  short_scale + theme(legend.position = "bottom") +
  geom_hline(yintercept = 0.5) +
  scale_fill_brewer(palette = article_palette,
                    labels = c("Female", "Male", "Unknown")) +
  article_theme
```

@@

ahr_proportions %>%
  ggplot(aes(x = year, y = proportion, fill = gender)) + 
  geom_bar(binwidth = 1, stat = "identity") +
  ggtitle("Authors of books reviewed in the AHR by gender") +
  xlab(NULL) + ylab(NULL) +
  theme(legend.position = "bottom") +
  geom_hline(yintercept = 0.5) +
  scale_fill_brewer(palette = article_palette,
                      labels = c("Female", "Male", "Unknown")) +
  article_theme
```

@@

```{r}
ahr_predicted %>%
  filter(gender_author == "male") %>%
  select(year, gender_reviewer) %>%  
  group_by(year, gender_reviewer) %>% 
  summarize(n = n()) %>% 
  spread(gender_reviewer, n, fill = 0) %>%
  mutate(female_proportion = female / (female + male + unknown),
         male_proportion = male / (female + male + unknown),
         unknown_proportion = unknown / (female + male + unknown)) %>%  
  select(female_proportion, male_proportion, unknown_proportion, year) %>%
  gather(gender, proportion, -year) %>%
  ggplot(aes(x = year, y = proportion, fill = gender)) + 
  geom_bar(binwidth = 1, stat = "identity") +
  ggtitle("Gender of reviewers of MALE book authors in AHR") +
  xlab(NULL) + ylab(NULL) +
  theme(legend.position = "bottom") +
  geom_hline(yintercept = 0.5) +
  scale_fill_brewer(palette = article_palette, 
                    labels = c("Female", "Male", "Unknown")) +
  article_theme +
  short_scale
```

```{r}
ahr_predicted %>%
  filter(gender_author == "female") %>%
  select(year, gender_reviewer) %>%  
  group_by(year, gender_reviewer) %>% 
  summarize(n = n()) %>% 
  spread(gender_reviewer, n, fill = 0) %>%
  mutate(female_proportion = female / (female + male + unknown),
         male_proportion = male / (female + male + unknown),
         unknown_proportion = unknown / (female + male + unknown)) %>%  
  select(female_proportion, male_proportion, unknown_proportion, year) %>%
  gather(gender, proportion, -year) %>%
  ggplot(aes(x = year, y = proportion, fill = gender)) + 
  geom_bar(binwidth = 1, stat = "identity") +
  ggtitle("Gender of reviewers of FEMALE book authors in AHR") +
  xlab(NULL) + ylab(NULL) +
  theme(legend.position = "bottom") +
  geom_hline(yintercept = 0.5) +
  scale_fill_brewer(palette = article_palette, 
                    labels = c("Female", "Male", "Unknown")) +
  article_theme +
  short_scale
```

>>>>

```{r}
diss_predicted %>%
  mutate(gender_author = factor(gender_author, 
                                levels = c("female", "unknown", "male"))) %>%
  ggplot(aes(x = year, fill = gender_author)) + 
  geom_bar(binwidth = 1) +
  ggtitle("Dissertations about history by gender, 1950-2012") +
  xlab(NULL) + ylab(NULL) +
  short_scale + theme(legend.position = "bottom") +
  scale_fill_brewer(palette = article_palette, name = "",
                      labels = c("Female", "Unknown", "Male")) +
  article_theme
```

@@

diss_proportions$gender <- factor(diss_proportions$gender, 
                                  levels = c("female_proportion", 
                                             "unknown_proportion", 
                                             "male_proportion"))

diss_proportions  %>%
  ggplot(aes(x = year, y = proportion, fill = gender, order = gender)) +
  geom_bar(binwidth = 1, stat = "identity") +
  ggtitle("Proportion of dissertations about history by gender, 1950-2012") +
  xlab(NULL) + ylab(NULL) +
  short_scale + theme(legend.position = "bottom") +
  geom_hline(yintercept = 0.5) +
  scale_fill_brewer(palette = article_palette,
                    labels = c("Female", "Unknown", "Male")) +
  article_theme
```

@@

ahr_proportions$gender <- factor(ahr_proportions$gender, 
                                 levels = c("female_proportion", 
                                            "unknown_proportion", 
                                            "male_proportion"))

ahr_proportions %>%
  ggplot(aes(x = year, y = proportion, fill = gender, order = gender)) + 
  geom_bar(binwidth = 1, stat = "identity") +
  ggtitle("Authors of books reviewed in the AHR by gender") +
  xlab(NULL) + ylab(NULL) +
  theme(legend.position = "bottom") +
  geom_hline(yintercept = 0.5) +
  scale_fill_brewer(palette = article_palette,
                      labels = c("Female", "Unknown", "Male")) +
  article_theme
```

@@

```{r}
ahr_predicted %>%
  filter(gender_author == "male") %>%
  select(year, gender_reviewer) %>%  
  group_by(year, gender_reviewer) %>% 
  summarize(n = n()) %>% 
  spread(gender_reviewer, n, fill = 0) %>%
  mutate(female_proportion = female / (female + male + unknown),
         male_proportion = male / (female + male + unknown),
         unknown_proportion = unknown / (female + male + unknown)) %>%  
  select(female_proportion, male_proportion, unknown_proportion, year) %>%
  gather(gender, proportion, -year) %>%
  mutate(gender = factor(gender, levels = c("female_proportion",
                                            "unknown_proportion",
                                            "male_proportion"))) %>%
  ggplot(aes(x = year, y = proportion, fill = gender, order = gender)) + 
  geom_bar(binwidth = 1, stat = "identity") +
  ggtitle("Gender of reviewers of MALE book authors in AHR") +
  xlab(NULL) + ylab(NULL) +
  theme(legend.position = "bottom") +
  geom_hline(yintercept = 0.5) +
  scale_fill_brewer(palette = article_palette, 
                    labels = c("Female", "Unknown", "Male")) +
  article_theme +
  short_scale
```

```{r}
ahr_predicted %>%
  filter(gender_author == "female") %>%
  select(year, gender_reviewer) %>%  
  group_by(year, gender_reviewer) %>% 
  summarize(n = n()) %>% 
  spread(gender_reviewer, n, fill = 0) %>%
  mutate(female_proportion = female / (female + male + unknown),
         male_proportion = male / (female + male + unknown),
         unknown_proportion = unknown / (female + male + unknown)) %>%  
  select(female_proportion, male_proportion, unknown_proportion, year) %>%
  gather(gender, proportion, -year) %>%
  mutate(gender = factor(gender, levels = c("female_proportion",
                                            "unknown_proportion",
                                            "male_proportion"))) %>%
  ggplot(aes(x = year, y = proportion, fill = gender, order = gender)) + 
  geom_bar(binwidth = 1, stat = "identity") +
  ggtitle("Gender of reviewers of FEMALE book authors in AHR") +
  xlab(NULL) + ylab(NULL) +
  theme(legend.position = "bottom") +
  geom_hline(yintercept = 0.5) +
  scale_fill_brewer(palette = article_palette, 
                    labels = c("Female", "Unknown", "Male")) +
  article_theme +
  short_scale
```
